Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-25 documents/BrazilSlides/slides.tex
Changed Section Headers
Slight improvements to the slides

\section{Quantum Non-locality From Inflation}

@@

\begin{frame}
    \frametitle{Fritz Distribution}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \quad \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2}
    \end{gather*}
    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
        M_{B} = \bc{\ket{0\psi_{6}}\bra{0\psi_{6}}, \ket{0\psi_{2}}\bra{0\psi_{2}}, \ket{1\psi_{0}}\bra{1\psi_{0}}, \ket{1\psi_{4}}\bra{1\psi_{4}}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Large Inflation}
    \begin{center}
        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{center}
\end{frame}

@@

@@

\section{Maximal Violations \& Noise}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        \item Computationally efficient
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing States}
    \begin{itemize}
        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
        \item For $d = 4$:
        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
        \item $d^2$ real-valued parameters
        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing States Cont'd}
    \begin{itemize}
        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
        \item Freedom to choice $k$
        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing POVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
        \item $n$-outcome measurement
        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
        \item Warrants consideration of \term{projective-valued measures (PVMs)}
    \end{itemize}
    \note<1>[item]{Naimark's Dilation Theorem}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Use unitary transformation again
        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
        \item PVMs are computationally more efficient
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}
\begin{frame}
    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
\end{frame}

@@

@@

\begin{frame}
    \frametitle{Noisy Non-locality}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 255} = 0.00133 \]
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{enumerate}
        \item Inflation technique capable of producing polynomial inequalities with quantum/classical witnesses
        \item Fritz witness-able by party-symmetric inequalities
        \item Maximally violating distributions require non-maximally entangled states
    \end{enumerate}
\end{frame}

@@

\section{Optional Slides}

@@

\section{Local Minima Concerns}

>>>>

\section{Part 2: Quantum Non-locality From Inflation}

@@

\begin{frame}
    \frametitle{Triangle Scenario As Bell Scenario}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational_fritz_bell}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_brazil.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution Bit-Measurements}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \quad \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2}
    \end{gather*}
    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
        M_{B} = \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Large Inflation}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{Symmetric Inequalities}
    \begin{itemize}
        \item Certificate inequalities are curated/constructed to witness violation of particular distribution
        \item Above inequality not the best candidate to search for non-locality different than Fritz distribution
        \item Perhaps one could obtain inequality that does not assign special preference to $C$
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
    \end{itemize}
\end{frame}

@@

\section{Part 3: Maximal Violations \& Noise}

@@

\begin{frame}
    \frametitle{Quantum Model On Triangle Scenario}
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
    \begin{center}
        \scalebox{0.6}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
    \begin{itemize}
        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite \textbf{qubit} state acting on $\Hilb^{2} \otimes \Hilb^{2}$
        \item Each party $\br{A, B, C}$ is assigned $4$-outcome PVM set $\br{M_A, M_B, M_C}$
        \item Parameterized using unitary transformations $U \in \s{U}\br{4}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} parameterization of $\s{U}\br{d}$
        \[ \la = \begin{pmatrix}
            \textcolor{Blue}{\la_{1,1}} & \textcolor{OliveGreen}{\cdots} & \textcolor{OliveGreen}{\la_{1, d}} \\
            \textcolor{Maroon}{\vdots} & \textcolor{Blue}{\ddots} & \textcolor{OliveGreen}{\vdots} \\
            \textcolor{Maroon}{\la_{d,1}} & \textcolor{Maroon}{\cdots} & \textcolor{Blue}{\la_{d, d}} \\
        \end{pmatrix} \]
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \textcolor{OliveGreen}{R_{m,n}} \textcolor{Maroon}{RP_{n,m}}}} \tcdot \bs{\prod_{l=1}^{d} \textcolor{Blue}{GP_{l}}} \]
        \item Global Phase Terms: \textcolor{Blue}{$GP_{l} = \exp\br{iP_l \lambda_{l,l}}$}
        \item Relative Phase Terms: \textcolor{Maroon}{$RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$}
        \item Rotation Terms: \textcolor{OliveGreen}{$R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$}
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        % \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
        \[ \ti{U} = \prod_{m=1}^{d} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
        \item Computationally efficient (no matrix exponentials)
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each part is assigned $d$ element \term{projective-valued measures (PVMs)} acting on $\s{H}^d$,
        \[ M = \bc{M_1, \ldots, M_d} \qquad \sum_{i=1}^{d} M_{i} = \ident \]
        \[ \forall i: \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_i \ket{\psi} \geq 0 \quad M_i = M_i^{\dagger} \]
        \[ M_{i}M_{j} = \de_{ij} M_{i} \quad M_{i} = \ket{m_{i}}\bra{m_{i}} \]
        % \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Unitary transform maps $M$ to computational basis
        \[ \bc{\ket{m_{1}}, \ldots, \ket{m_{d}}} = \bc{U \ket{1}, \ldots, U \ket{d}} \]
        \item Global phase irrelevant: $\ti{U}$ requires $d(d - 1)$ real-valued parameters
        \item PVMs are computationally more efficient than POVMs
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}

\begin{frame}
    \frametitle{Parameterizing States}
    \begin{itemize}
        \item Exploit spectral decomposition
        \[ \rho = \sum_{i=1}^{d} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
        \item Unitary transform maps $\bc{\ket{\psi_i}}$ to computational basis
        \[ \bc{\ket{\psi_{1}}, \ldots, \ket{\psi_{d}}} = \bc{U \ket{1}, \ldots, U \ket{d}} \]
        \item Global phase irrelevant again $\ti{U}$ requires $d\br{d - 1}$ real-valued parameters
        \item Eigenvalues $\bc{p_i}$ parameterized using hyper-spherical coordinates: $d - 1$ real-valued parameters
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
\end{frame}

@@

\begin{frame}
    \frametitle{Noisy Non-locality}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 243} = 0.00133 \]
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{enumerate}
        \item \textbf{Inflation technique} capable of producing polynomial inequalities with quantum/classical witnesses
        \item Fritz witness-able by \textbf{party-symmetric inequalities}
        \item Maximally violating distributions require \textbf{non-maximally entangled states}
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Unanswered Questions}
    \begin{enumerate}
        \item Do these new non-local distributions suggest \textbf{new quantum resources} in the triangle scenario?
        \item Can any non-local quantum correlations in the triangle scenario \textbf{satisfy CHSH inequalities} (under Fritz type coarse graining)?
        \item Which inequalities are \textbf{most robust} to noise? Facets?
    \end{enumerate}
\end{frame}

@@

\section{Appendix A: Optional Slides}

@@

\begin{frame}
    \frametitle{Parameterizing POVMs [Optional]}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
        \item $n$-outcome measurement
        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
        \item Warrants consideration of \term{projective-valued measures (PVMs)}
    \end{itemize}
    \note<1>[item]{Naimark's Dilation Theorem}
\end{frame}

\begin{frame}
    \frametitle{Cholesky Parameterization of States [Optional]}
    \begin{itemize}
        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
        \item For $d = 4$:
        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
        \item $d^2$ real-valued parameters
        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
    \end{itemize}
\end{frame}

\section{Appendix B: Local Minima Concerns}
